---
title: "hw6_p8105_zl2978"
author: "Zhiye Lou"
date: "12/7/2020"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(modelr)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# Problem 1   
I will first read the data and start with one city.
```{r}
homicide = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
baltimore =
  homicide %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```

Now I will do it for multiple cities and create a plot.
```{r}
models_results_df = 
  homicide %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

# Problem 2  
I will first read and tidy the data.   
```{r}
birthweight = 
  read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(babysex = recode(babysex, "1" = "male", "2" = "female"),
         frace = recode(frace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other", "9" = "Unknown"),
         malform = recode(malform, "0" = "absent", "1" = "present"),
         mrace = recode(mrace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other"))
number_of_na = sum(is.na(birthweight))
check_incomelete = sum(!complete.cases(birthweight))
```
I will first use a backward stepwise to choose my factors.   
```{r}
fit1 = 
  lm(bwt ~ ., data = birthweight) %>% 
  step(direction = "backward", trace = 0) 
fit1 %>% 
  broom::tidy() %>% 
  knitr::kable()
```
My predictors are babysex, bhead, blength, delwt, fincome, gaweeks, mheight, mrace, parity, ppwt and smoken.  
My model was selected by using the backward stepwise, and then I will make a plot of model residuals against fitted values.  
```{r}
birthweight %>% 
    add_predictions(fit1) %>% 
    add_residuals(fit1) %>% 
    ggplot(aes(x = pred, y = resid)) +
        geom_point()  + 
    geom_smooth() + 
    labs(title = "Predicted vs Residuals", 
       x = "Predicted", 
       y = "Residuals")
```

