---
title: "hw6_p8105_zl2978"
author: "Zhiye Lou"
date: "12/7/2020"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(modelr)
knitr::opts_chunk$set(
	echo = TRUE,
	fig.height = 6,
	fig.width = 8,
	message = FALSE,
	warning = FALSE,
	out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# Problem 1   
I will first read the data and start with one city.
```{r}
homicide = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
baltimore =
  homicide %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```

Now I will do it for multiple cities and create a plot.
```{r}
models_results_df = 
  homicide %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

# Problem 2  
I will first read and tidy the data.   
```{r}
birthweight = 
  read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(babysex = recode(babysex, "1" = "male", "2" = "female"),
         frace = recode(frace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other", "9" = "Unknown"),
         malform = recode(malform, "0" = "absent", "1" = "present"),
         mrace = recode(mrace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other"))
number_of_na = sum(is.na(birthweight))
check_incomelete = sum(!complete.cases(birthweight))
```
I will first use a backward stepwise to choose my factors.   
```{r}
fit1 = 
  lm(bwt ~ ., data = birthweight) %>% 
  step(direction = "backward", trace = 0) 
fit1 %>% 
  broom::tidy() %>% 
  knitr::kable()
```
My predictors are babysex, bhead, blength, delwt, fincome, gaweeks, mheight, mrace, parity, ppwt and smoken.  
My model was selected by using the backward stepwise, and then I will make a plot of model residuals against fitted values.  
```{r}
birthweight %>% 
    add_predictions(fit1) %>% 
    add_residuals(fit1) %>% 
    ggplot(aes(x = pred, y = resid)) +
        geom_point()  + 
    geom_smooth(method = "lm") + 
    labs(title = "Predicted vs Residuals", 
       x = "Predicted", 
       y = "Residuals")
```
As we can see, the residuals are almost symmetrical to 0, and there is no obvious relationship between the predicted value since the points are clustered together and the line is almost flat.  

Then I will compare my model to two other models.  
```{r}
## length at birth and gestational age as predictors (main effects only)
fit2 = lm(bwt ~ blength + gaweeks, data = birthweight) 
fit2 %>% 
  broom::tidy() %>% 
  knitr::kable()
## One using head circumference, length, sex, and all interactions (including the three-way interaction)
fit3 = lm(bwt ~ bhead * blength * babysex, data = birthweight) 
fit3 %>% 
  broom::tidy() %>% 
  knitr::kable()
```

I will make the comparison by cross-validation.
```{r}
cv_birthweight = 
    crossv_mc(birthweight, 200) %>% 
    mutate(
        train = map(train, as.tibble),
        test = map(test,as.tibble)
    ) %>% 
   mutate(
        my_model = map(train,~fit1),
        model1 = map(train,~fit2),
        model2 = map(train,~fit3)
    ) %>% 
    mutate(
        rmse_my_model = map2_dbl(my_model, test, ~rmse(model = .x,data = .y)),
        rmse_model1 = map2_dbl(model1, test, ~rmse(model = .x,data = .y)),
        rmse_model2 = map2_dbl(model2, test, ~rmse(model = .x,data = .y))
    )
cv_birthweight %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```
As the plot shown, my_model has the best distribution of RMSE, and the model with main effect only has the worst distribution of RMSE.

# Problem 3  